```{r}
f<-read.csv('Llaabb-4.csv',header=TRUE)
f
```

Change the column names of faculty data set. 
```{r}
colnames(f)<-c("Names","Desig","Sal","Department","Trainings","Papers","Gender")
summary(f)

```

Use map values() , as.factor() and transform ()
??? to change the designation column to have numerical values. 1- Prof, 2-Asso.Prof,3-Asst.Prof;
??? to change gender column 1-Male, 2-Female
```{r}
library(plyr)
f<-transform(f,
             Desig=as.factor(mapvalues(Desig,c("Professor","Assosciate Professor","Assistant Professor"),c(1,2,3))),
             Gender=as.factor(mapvalues(Gender,c("M","F"),c(1,2))))
f

```

Using with() and tapply() , calculate the mean training programs attended and no. of papers published in each department. Format it for markdown.
```{r}
library(knitr)
library(rmarkdown)
kable(with(f,tapply(Trainings, INDEX=list(Department,Papers),FUN=mean)),format="markdown")


kable(with(f,tapply(Trainings, INDEX=list(Department,Gender),FUN=mean)),format="markdown")

kable(with(f,tapply(Papers, INDEX=list(Department,Gender),FUN=sum)),format="markdown")
```

Using with() and aggregate() , calculate the mean training programs attended and no. of papers published in each department. Format it for markdown.
```{r}
kable(with(f,aggregate(Trainings,by=list(Department,Papers),FUN=mean)),format="markdown")

kable(with(f,aggregate(Trainings,by=list(Department,Gender),FUN=mean)),format="markdown")

kable(with(f,aggregate(Papers,by=list(Department,Gender),FUN=sum)),format="markdown")
```

Check whether the mean value of no. of papers published in depts. are influenced by training programs attended and designation. Do regression analysis using aggregate().
```{r}
aggregate(Papers~Trainings+Desig,FUN=mean, data=f)

```

Create the table output for designation and papers published. Use with() and table().
```{r}
ans<-with(f,table(Papers,Desig))
ans
```

Find the odds of lower no. of paper published with respect to designation and no.of training programs attended using the output of question (f).
```{r}
ans.or<-as.numeric(ans[1,1])/as.numeric(ans[1,2])/as.numeric(ans[1,3])/as.numeric(ans[2,1])/as.numeric(ans[2,2])/as.numeric(ans[2,3])/as.numeric(ans[3,1])/as.numeric(ans[3,2])/as.numeric(ans[3,3])/as.numeric(ans[4,1])/as.numeric(ans[4,2])/as.numeric(ans[4,3])/as.numeric(ans[5,1])/as.numeric(ans[5,2])/as.numeric(ans[5,3])/as.numeric(ans[6,1])/as.numeric(ans[6,2])/as.numeric(ans[6,3])
ans.or
```

Is the designation affects the training programs attended? Check it with the data. Prove it
```{r}
with(f,cor(as.numeric(Desig), Trainings))

```

Find the correlation of papers published and training programs attended using with(), cor().
```{r}
with(f,cor(Papers, Trainings))

```

Find the correlation of training programs attended and designation using with(), cor().
```{r}

with(f,cor(Trainings,as.numeric(Desig)))
```

Using by() combine the operations of above questions (i) and (j) using function. And do the correlation analysis using cor() with in the function.
```{r}
by(data = f[c("Papers", "Trainings")], 
   INDICES = f["Desig"], 
   FUN = function(x) {cor(x[,1], x[,2])})

```

Plot average training programs attended against designations(only 3 designations) of the institution using plot()
```{r}
plot(f$Desig, f$Trainings)

```

Plot average papers published against designations of the institution using plot().
```{r}
plot(f$Desig, f$Papers)
```

Change the x axis , color and y-axis labels respectively. Add legends. 
```{r}
plot(f$Desig, f$Papers,xlab="Designation",ylab="Papers Published",col=3,main="Designation vs Papers Published")

```

Plot the above graphs in (l) and (m) using with() and plot().
```{r}
par(mfrow = c(1,2))
with(f, plot(Desig, Trainings, 
                   main = "Designation vs Trainings", 
                   xlab = "Designation", 
                   ylab = "Tranings",col=7))
with(f, plot(Desig, Papers, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=8))


```

Draw scatter plot for above questions. Draw box plot for above question. Draw bar plots for above questions. Draw single variable plots for above question.
```{r}
par(mfrow = c(1,2))
with(f, plot(as.numeric(Desig), Trainings, 
                   main = "Designation vs Trainings", 
                   xlab = "Designation", 
                   ylab = "Tranings",col=1))
with(f, plot(as.numeric(Desig), Papers, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=2))



```




```{r}

with(f,plot(Trainings))

```

plot the prof, asst.prof and asso.prof average performance in different colors using rep(), colorpalatte functions. Represent each designation average performance(no.of.papers published and training pgms atteneded) by different symbols.
```{r}

```

