```{r}
faculty<-read.csv('Q1b.csv',header=TRUE)
head(faculty)

```

a. extract each dept faculty details separately
```{r}
aggregate(Name~Dept,data=faculty,toString)
```

b. extract Professors of each dept seperately
```{r}
prof<-faculty[faculty$Designation=="Professor",c("Name","Dept")]
aggregate(Name~Dept,data=prof,toString)
```

c. extract people who earn more than 1.5 lakh in each dept where their designation is prof,associate or assistant
```{r}
ppl<-faculty[faculty$Salary>150000,c("Name","Dept")]
aggregate(Name~Dept,ppl,toString)

```

d.Find out the cost of professors in each dept .(sum up their salary to get cost of them)
```{r}
prof=faculty[faculty$Designation=="Professor",]
aggregate(Salary~Dept,prof,sum)


```

e. Find the cost of each dept faculty
```{r}
aggregate(Salary~Dept,faculty,sum)

```

f. Find out the average cost of faculty in each dept.
```{r}
aggregate(Salary~Dept,faculty,mean)
```

g.Which dept has highest average cost of faculty
```{r}
avg_sal<-aggregate(Salary~Dept,faculty,mean)
avg_sal[which.max(avg_sal$Salary),]

```

i. Which dept has lowest cost of faculty
```{r}
val<-aggregate(Salary~Dept,faculty,mean)
val[which.min(val$Salary),]


```

