```{r}

faculty<-read.csv('Q3a.csv',header = TRUE)
head(faculty)
```

a. Store faculty salary numerically, transform into factor.( eg. 50000 to 75000 as 1, 75000 to 100000 as 2 , and so on)
```{r}
fac_cut<-cut(faculty$Salary, breaks=c(50000, 75000, 100000, 125000,150000,175000,200000,Inf))
str(fac_cut)

```

b. Check whether faculty paper publication count and number of training program
attended are same or not.
```{r}
identical(faculty$Papers.Published,faculty$Training)

```

c. Extract paper published count separately. If the count is grater than 15 map it as "Excellent", if it is (10-15 )map it as "good", if it is (5 to 10) map it as " moderate"), if it is (1-5) map it as "need to improve", else "poor, start your research".
```{r}
assignComment <- function(x) 
{
 if(x >= 15) {
    res <- "Excellent"
  } else if(x >= 10 & x<15) {
    res <- "Good"
  } else if(x >= 5 & x<10) {
    res <- "Moderate"
  } else if(x>=1 & x<5){
    res <- "Need to improve"
  }
  else{
    res<-"Poor,start your research"
  }
  res
}

for(i in 1:nrow(faculty))
{
 papers<-faculty[i,"Papers.Published"]
 ans<-assignComment(papers)
 faculty[i,"Comment"]<-ans
 }
 
faculty
```

d. Consider the solution of 1c. Map "Excellent", "good" as " Good performers".
Map " Moderate" and "need to improve" as " Ok, Keep it up". Else " map to " You may be fired!"
```{r}
assignImplication <- function(x) 
{
 if(x =="Excellent"| x=="Good") {
    res <- "Good Perfformers"
  } else if(x =="Moderate" | x=="Need to improve") {
    res <- "Ok,Keep it up"
  } 
  else{
    res<-"You may be fired!"
  }
  res
}
for(i in 1:nrow(faculty))
{
 comment<-faculty[i,"Comment"]
 ans<-assignImplication(comment)
 faculty[i,"Implication"]<-ans
 }
 
faculty

```

e. Transform designations to numerical data
```{r}
fac1<-transform(faculty,Designation=as.numeric(Designation))
fac1

```

f. Using factor() and mapvalues() convert designations to numerical data.
```{r}
fac2<-transform(faculty,Designation=as.factor(mapvalues(Designation,c("Professor","Assistant Professor","Assosciate Professor"),c(1,2,3))))
fac2

```

g. create table for faculty names and designations.
```{r}
table(faculty$Name,faculty$Designation)

```

h.Write separate functions to perform all the above functions separately and call them in R script.

i. Write a function to perform statistical analysis of faculty data to identify faculty performance of depts.
```{r}

Summary_fac <- function(x) {
  ans<-c(mean=mean(x), median=median(x), sd=sd(x))
  ans
}

f<-faculty[faculty$Dept=="CSE",]
ans<-Summary_sub(f$Papers.Published)
ans

f1<-faculty[faculty$Dept=="ISE",]
ans<-Summary_sub(f1$Papers.Published)
ans
```

j. Use sapply to perform all the above functions.
```{r}
assignComment <- function(x) 
{
 if(x >= 15) {
    res <- "Excellent"
  } else if(x >= 10 & x<15) {
    res <- "Good"
  } else if(x >= 5 & x<10) {
    res <- "Moderate"
  } else if(x>=1 & x<5){
    res <- "Need to improve"
  }
  else{
    res<-"Poor,start your research"
  }
  res
}


 papers<-faculty[,"Papers.Published"]
 ans<-sapply(papers,FUN=assignComment)
 f<-data.frame(faculty$Name,ans)
 
 
f
```

```{r}
assignImplication <- function(x) 
{
 if(x =="Excellent"| x=="Good") {
    res <- "Good Perfformers"
  } else if(x =="Moderate" | x=="Need to improve") {
    res <- "Ok,Keep it up"
  } 
  else{
    res<-"You may be fired!"
  }
  res
}

 comment<-faculty[,"Comment"]
 ans<-sapply(comment,FUN=assignImplication)
 f2<-data.frame(faculty$Name,ans)
 
 
f2
```

