```{r}
faculty<-read.csv('Q3a.csv',header=TRUE)
head(faculty)
```

Plot, in each dept, how many faculty are earning more than 1 lakh.
```{r}
f<-faculty[faculty$Salary>100000,c("Name","Dept")]
f
plot(table(f$Dept))

```

create subset of faculty, who have published more than 10 papers and their designation is Associate professor.
```{r}
sub<-subset(faculty,Designation=="Assosciate Professor" & Papers.Published>4)
sub

```

Find out average papers published by each dept, designation wise
```{r}
a<-aggregate(Papers.Published~Dept+Designation,faculty,mean)
a
```

Find out Average training programs attended by faculty each dept wise.
```{r}
aggregate(Training~Dept,faculty,mean)

```

v. Extract top 3 performers among faculty dept wise(more papers published and more
training programmes attended)
```{r}

```

vi. Sort faculty details , dept wise separately
```{r}
faculty[order(faculty$Dept,faculty$Name),]

```

vii. Search for faculty name in the data set and retrive his/her details
```{r}
subset(faculty,Name=="Mithra")

```

