```{r}
stud<-read.csv('Q8a.csv',header=TRUE)
head(stud)

```

a. Change the column names of stud data set. 
```{r}
colnames(stud)<-c("Name","USN","Department","S1","S2","S3","S4","S5","SGPA","Gender")
head(stud)

```

b. Use with() and plot(), plot graph against dept and average CGPA semesterwise.
```{r}
s<-aggregate(SGPA~Department,stud,mean)
s
with(s,plot(Department,SGPA,ylim=c(0,10)))
```

c. Use qplot(), to plot the same mentioned in (b)
```{r}
library('ggplot2')
qplot(s$Department,s$SGPA)

```

d. Use qplot() with attributes color, shape, x and y labels.
```{r}
qplot(s$Department,s$SGPA,xlab="Department",ylab="Average SGPA",colour='red')

```

e. Display the dimension of stud data set.
```{r}
nrow(stud)
ncol(stud)

```

f. using ggplot() and geom_point() , plot the same mentioned in (b)
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point()

```

g. in ggplot() , change the point size.
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point(aes(size=4))

```
h. change color of points in ggplot().
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point(colour="green")
```

i. define your own color palatte and use it in ggplot()
```{r}
cbpallete<-c('#E69F00','#F6B4E9','#009E73','#F0EE22','#F00000','#Eff000','#345670','#FFFF00','#098766')
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point(colour=cbpallete)


```

j. Using facet_wrap(), plot for (f), with respect to dept
```{r}

ggplot(data=s,aes(x=Department,y=SGPA))+geom_point()+facet_wrap(~Department)
```

k. Using facet_grid(), perform the (j)
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point()+facet_grid(~Department)
```

l. Draw bar graph for (b) using ggplot and geom_bar().
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_bar(stat = "identity")
```

m. Add legends in graph.
```{r}
c9<-c("BT","CHEM","CSE","ECE","EEE","IEM","ISE","MECH","TCE")

ggplot(data=s,aes(x=Department,y=SGPA,fill=c9))+geom_bar(stat = "identity")

```

n. Draw smooth curves using stat_smooth() and by changing size for (b)
```{r}
s2<-aggregate(SGPA~Department+Gender,stud,mean)
s2
ggplot(data=s2,aes(x=Department,y=SGPA))+geom_line(size=2)+stat_smooth()
```

o. Add title to ggplot() of your graph and draw regression lines and geom points for (b)
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point()+ggtitle("Dept vs SGPA")
```

p. Draw ggplot() for dept wise students' average CGPA.
```{r}
ggplot(data=s,aes(x=Department,y=SGPA))+geom_point()
```

q. Draw grom Polygon for (p)



