```{r}
f<-read.csv('Q9a.csv',header=TRUE)
head(f)

```

a. Change the column names of faculty data set. 
```{r}
colnames(f)<-c("Names","Desig","Salary","Dept","Trainings","Papers")
head(f)

```

b. Use with() and plot(), plot graph against dept and average Papers published.
```{r}
f1<-aggregate(Papers~Dept,f,mean)
f1
with(f1,plot(x=Dept,y=Papers))

```
c. Use qplot(), to plot the same mentioned in (b)
```{r}
library('ggplot2')
qplot(f1$Dept,f1$Papers)

```

d. Use qplot() with attributes color, shape, x and y labels.
```{r}
qplot(f1$Dept,f1$Papers,xlab="Department",ylab="Average Papers",colour="red",shape=factor(f1$Dept))

```

e. Display the dimension of faculty data set.
```{r}
nrow(f)
ncol(f)
```

f. using ggplot() and geom_point() , plot the same mentioned in (b)
```{r}
ggplot(data=f1,aes(x=Dept,y=Papers))+geom_point()

```

g. in ggplot() , change the point size.
```{r}
ggplot(data=f1,aes(x=Dept,y=Papers))+geom_point(size=2)

```

h. change color of points in ggplot().
```{r}

ggplot(data=f1,aes(x=Dept,y=Papers))+geom_point(size=2,colour="purple")
```

i. define your own color palatte and use it in ggplot()
```{r}
cbpallete<-c('#E69F00','#F6B4E9','#009E73','#F0EE22')
ggplot(data=f1,aes(x=Dept,y=Papers))+geom_point(colour=cbpallete)

```

j. Using facet_wrap(), plot for (f), with respect to desgination.(Prof, Asso prof, Asst Prof)
```{r}
f2<-aggregate(Papers~Dept+Desig,f,mean)
f2
ggplot(data=f2,aes(x=Dept,y=Papers))+geom_point()+facet_wrap(~Desig)
```

k. Using facet_grid(), perform the (j)
```{r}
ggplot(data=f2,aes(x=Dept,y=Papers))+geom_point()+facet_grid(.~Desig)
```

l. Draw bar graph for (b) using ggplot and geom_bar().
```{r}
ggplot(data=f1,aes(x=Dept,y=Papers))+geom_bar(stat="identity")
```

m. Add legends in graph.
```{r}
c4<-c("CSE","ISE","MECH","TCE")
ggplot(data=f1,aes(x=Dept,y=Papers,fill=c4))+geom_bar(stat="identity")
```

n. Draw smooth curves using stat_smooth() and by changing size for (b).
```{r}

f2<-aggregate(Papers~Dept+Desig,f,mean)
f2
ggplot(data=f2,aes(x=Dept,y=Papers))+geom_line()+stat_smooth()

```

o. Add title to ggplot() of your graph and draw regression lines and geom points for (b)
```{r}
ggplot(f1,aes(x=Dept,y=Papers)) + ggtitle("Average Papers per Dept")+geom_point()
  
```

p. Draw ggplot() for dept wise average training programs attened by Asst prof.
```{r}
f3<-f[f$Desig=="Assistant Professor",]
f4<-aggregate(Trainings~Dept,f3,mean)
f4
ggplot(f4,aes(x=Dept,y=Trainings))+geom_point()

```

q. Draw grom Polygon for (p)
```{r}

```

