```{r}

student<-read.csv("Tut-3.csv",header=TRUE)
head(student$Sub2,10)
```

```{r}
str(student)
#Sub2 is becoming factors as they contain String data
```

Convert the marks to numerical data and show.
```{r}
sub2<-student$Sub2
sub2

as.numeric(as.character(sub2))

```

Display the mark as factors.
```{r}
as.numeric(sub2)

```

 Display the marks as characters
```{r}
 as.character(sub2)
```
Display the type of marks columns
```{r}
typeof(as.numeric(as.character(sub2)))

```

using gsub remove character data in marks column. Using gsub remove numerical data in name column
```{r}
sub2
gsub("[^0-9]","",sub2)
names<-student$ï..Names
gsub("[^A-Za-z]","",names)
```

Clean the name and marks column and put it in a new student data set variable using transform function
```{r}
sub2.clean <- as.numeric(gsub("[^0-9.]", "", sub2))
sub2.clean
new_stud<-transform(student, Sub2 = sub2.clean)
new_stud

```

use table to get summary of student data
```{r}
table(student["Sub1"])
table(student["Dept"])
```

Use sapply to perform the cleaning of data mentioned above
```{r}
clean<-function(student)
{
  sub2.clean <- as.numeric(gsub("[^0-9.]", "", sub2))
  sub2.clean
  new_stud<-transform(student, Sub2 = sub2.clean)
  new_stud
}

sapply(student,FUN=clean)
```

 use lapply to perform the cleaning of data mentioned above
```{r}
clean<-function(student)
{
  sub2.clean <- as.numeric(gsub("[^0-9.]", "", sub2))
  sub2.clean
  new_stud<-transform(student, Sub2 = sub2.clean)
  new_stud
}

lapply(student,FUN=clean)

```

Display the summary using summary()
```{r}
summary(student)

```

Include gender details for students.Add Mr or Ms. For each student, using paste command . Display all students details.
```{r}

```

Define user defined functions to perform the above operations.
```{r}
naming<-function(Gender)
{
  
  if(Gender=='F')
    res="Mrs "
  else
    res="Mr "
  res
}
names=student$Gender
res<-sapply(names,FUN=naming)
d<-data.frame(res,student)
d
```

Use while loop, for loop to access students marks and find the grades. Put this with in a function
```{r}
grade<-function(s1,s2,s3,s4,s5)
{

  tot<-(s1+s2+s3+s4+s5)/5
  if(tot>=90)
    res<-"S"
  else if(tot>=75)
    res<-"A"
  else if(tot>=60)
    res<-"B"
  else if(tot>=50)
    res<-"C"
  else
    res<-"F"
  res
}

for(i in 1:nrow(student))
{
  
  
  s1<-as.numeric(student[i,"Sub1"])
  
  s2<-as.numeric(student[i,"Sub2"])
  
  s3<-as.numeric(student[i,"Sub3"])
  
  s4<-as.numeric(student[i,"Sub4"])
  
  s5<-as.numeric(student[i,"Sub5"])
  g<-grade(s1,s2,s3,s4,s5)
  print(as.character(student[i,"ï..Names"]))
  print(g)
  
}
```

Use apply, sapply, lapply and tapply to perform the above operation over all the columns of students
data set.
```{r}
grade<-function(s1)
{

  tot<-sum(s1)/5
  if(tot>=90)
    res<-"S"
  else if(tot>=75)
    res<-"A"
  else if(tot>=60)
    res<-"B"
  else if(tot>=50)
    res<-"C"
  else
    res<-"F"
  res
}

mark<-c(as.numeric(student[1,"Sub1"])+as.numeric(student[1,"Sub2"])+as.numeric(student[1,"Sub3"])+as.numeric(student[1,"Sub4"])+as.numeric(student[1,"Sub5"]))
sapply(mark,FUN=grade)
lapply(mark,FUN=grade)
tapply(mark,FUN=grade,INDEX=1)
```

Use with() function to apply the above operation over students dataset.
```{r}

```

Use any() function to apply the above operation over students dataset.
```{r}

```

