```{r}

s<-read.csv('Tut-4.csv',header=TRUE)
s
```

Change the column names of Student data set. 
```{r}
colnames(s)<-c("Name","Stud_USN","Stud_Dept","S1","S2","S3","S4","S5","Stud_Grade","Stud_Gender","Stud_CGPA")
summary(s)

```

Use map values() , as.factor() and transform ()
. To change the Grade column(S,A,B,etc) to have numerical values. 1- S, 2-A,           3-B,etc.;
. To change gender column 1-Male, 2-Female
```{r}
library(plyr)
s<-transform(s,
             Stud_Grade=as.factor(mapvalues(Stud_Grade,c("S","A","B","C","D","E","F"),c(1,2,3,4,5,6,7))),
             Stud_Gender=as.factor(mapvalues(Stud_Gender,c("M","F"),c(1,2))))
s

```

Using with() and tapply() , calculate the mean of marks in each subject scored by students in each
department and mean of CGPA of students in each dept with respect to gender. Format it for markdown
```{r}
library(knitr)
library(rmarkdown)
kable(with(s,tapply(S1, INDEX = list(Stud_Dept,Stud_Gender), FUN=mean)),format="markdown")
kable(with(s,tapply(S2, INDEX = list(Stud_Dept,Stud_Gender), FUN=mean)),format="markdown")
kable(with(s,tapply(S3, INDEX = list(Stud_Dept,Stud_Gender), FUN=mean)),format="markdown")
kable(with(s,tapply(S4, INDEX = list(Stud_Dept,Stud_Gender), FUN=mean)),format="markdown")
kable(with(s,tapply(S5, INDEX = list(Stud_Dept,Stud_Gender), FUN=mean)),format="markdown")

kable(with(s,tapply(Stud_CGPA, INDEX = list(Stud_Dept,Stud_Gender) , FUN=mean)),format="markdown")
```

Using with() and aggregate() , calculate the mean of marks in each subject scored by students in each department and the gender of students in each dept. Format it for markdown.
```{r}
kable(with(s,aggregate(S1,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S2,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S3,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S4,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S5,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")

```

Check whether the mean value of each subject marks in depts influenced by the gender of students in each dept or not. Do regression analysis using aggregate().
```{r}
aggregate(S1~Stud_Gender,FUN=mean, data=s)
aggregate(S2~Stud_Gender,FUN=mean, data=s)
aggregate(S3~Stud_Gender,FUN=mean, data=s)
aggregate(S4~Stud_Gender,FUN=mean, data=s)
aggregate(S5~Stud_Gender,FUN=mean, data=s)

```

Create the table output for mean scores in subjects in each dept gender wise. Use with() and table().
```{r}

ans<-with(s,table(S1,Stud_Gender))
ans
```

Find the odds of lower no. of mean marks in subjects with respect to gender of students in the depts using the output of question (f).
```{r}
ans.or<-as.numeric(ans[1,1])/as.numeric(ans[1,2])/as.numeric(ans[2,1])/as.numeric(ans[2,2])/as.numeric(ans[3,1])/as.numeric(ans[3,2])/as.numeric(ans[4,1])/as.numeric(ans[4,2])/as.numeric(ans[5,1])/as.numeric(ans[5,2])/as.numeric(ans[6,1])/as.numeric(ans[6,2])/as.numeric(ans[7,1])/as.numeric(ans[7,2])/as.numeric(ans[8,1])/as.numeric(ans[8,2])
ans.or
```

Is the Gender of students affects the CGPA of students? Check it with the data. Prove it.
```{r}
with(s, cor(Stud_CGPA, as.numeric(Stud_Gender)))

```

Find the correlation of Gender of students and Marks and CGPA scored using with(), cor().
```{r}
with(s,cor(Stud_CGPA[Stud_Gender==1],S1[Stud_Gender==1]))
with(s,cor(Stud_CGPA[Stud_Gender==2],S1[Stud_Gender==2]))

```

Using by() combine the operations of above questions (i) and (j) using function. And do the correlation analysis using cor() with in the function.
```{r}
by(data = s[c("S1", "Stud_CGPA")], 
   INDICES = s["Stud_Gender"], 
   FUN = function(x) {cor(x[,1], x[,2])})

```

Plot average marks in subjects , CGPA scored against depts of the institution using plot()
```{r}
par(mfrow = c(1,2))
plot(s$Stud_Dept,s$Stud_CGPA)
plot(s$Stud_Dept,s$S1)

```

Plot average marks in subjects , CGPA scored against gender in each dept of the institution using plot().
```{r}
par(mfrow = c(1,2))
plot(s$Stud_Gender,s$S1)
plot(s$Stud_Gender,s$Stud_CGPA)

```

Change the x axis , color and y-axis labels respectively. Add legends. 
```{r}
par(mfrow = c(1,2))
plot(s$Stud_Gender,s$S1,xlab="Gender",ylab="Sub 1",col=2)
plot(s$Stud_Gender,s$Stud_CGPA,xlab="Gender",ylab="CGPA",col=6)

```

Plot the above graphs in (l) and (m) using with() and plot().
```{r}
par(mfrow = c(1,2))
with(s, plot(Stud_Gender, S1, 
                   main = "Gender vs Sub 1", 
                   xlab = "Gender", 
                   ylab = "Sub1",col=7))
with(s, plot(Stud_Gender, Stud_CGPA, 
                   main = "Gender vs CGPA", 
                   xlab = "Gender", 
                    ylab = "CGPA",col=8))

```

Draw scatter plot for above questions. Draw box plot for above question. Draw bar plots for above questions. Draw single variable plots for above question.
```{r}
par(mfrow = c(1,2))
with(s, plot(as.numeric(Stud_Gender), S1, 
                   main = "Gender vs Sub 1", 
                   xlab = "Gender", 
                   ylab = "Sub1",col=7))
with(s, plot(as.numeric(Stud_Gender), Stud_CGPA, 
                   main = "Gender vs CGPA", 
                   xlab = "Gender", 
                    ylab = "CGPA",col=8))

```

```{r}
with(s,plot(S1))

```

plot the female students and male students performance in different colors using rep(), colorpalatte functions. Represent each gender's average performance(dept wise) by different symbols.
```{r}

```

